The Unicode Cookbook \linebreak for Linguists

### 2017-12-15 book/chapters/ipa_background.tex
fixes issue #5

Several styles of transcription with the IPA are possible, as illustrated in the
\textit{Handbook}, and they are all valid.\footnote{For an illustration of
the differences, see the 29 languages and their transcriptions in the
\textit{Illustrations of the IPA}\citep[41--154]{IPA2007}.} Therefore, there are 
different but equivalent transcriptions, or as noted by \citet[64]{Ladefoged1990a}, 
``perhaps now that the Association has been explicit in its eclectic approach, outsiders to the
Association will no longer speak of \textit{the} IPA transcription of a given
phenomenon, as if there were only one approved style.'' Clearly not all
phoneticians agree, nor are they likely to ever completely agree, on all aspects of the
IPA or on transcription approaches and practices in general. As noted above, 
there have been several revisions in the IPA's long history, but the current version (2005) is
strikingly similar to the 1926 version, which shows the viability of the IPA as a
common standard for linguistic transcription.

>>>>

Several styles of transcription with the IPA are possible, as illustrated in the
\textit{Handbook}, and they are all valid.\footnote{For an illustration of
the differences, see the 29 languages and their transcriptions in the
\textit{Illustrations of the IPA} \citep[41--154]{IPA2007}.} Therefore, there are 
different but equivalent transcriptions, or as noted by \citet[64]{Ladefoged1990a}, 
``perhaps now that the Association has been explicit in its eclectic approach, outsiders to the
Association will no longer speak of \textit{the} IPA transcription of a given
phenomenon, as if there were only one approved style.'' Clearly not all
phoneticians agree, nor are they likely to ever completely agree, on all aspects of the
IPA or on transcription approaches and practices in general. As noted above, 
there have been several revisions in the IPA's long history, but the current version (2005) is
strikingly similar to the 1926 version, which shows the viability of the IPA as a
common standard for linguistic transcription.
